Cognitive Principles and Individual Differences \\ in Human Syllogistic Reasoning

### 2019-11-10 paper/paper-v3.tex
Improvements/suggestions

@@

% Yet, the cognitive adequacy of a theory can only be measured, if that theory is evaluable, i.e.\ if the theory can uniformally account for episodes of human reasoning systematically, according to its underlying assumptions. 
% Only then, the cognitve adequacy of that theory can be compared to others.
% 
% Formal methods can offer the required tools to implement such cognitive theories. This in turn, can allow a new way of communication among the fields, by avoiding ambiguous definitions, showing their formal correspondences and finally providing appropriate evaluation methods with respect to their cognitive adequacy. 
% A major drawback of 
The results of the meta-study on syllogistic reasoning in~\cite{khemlani:2012} show that the answers given by humans doe not only systematically differ from the valid conclusions under CL, but from any other proposed cognitive theory (cf.~\cite{BJ89,johnsonlaird:1983,Rips1994,Polk1995,chater:oaksford:1999}).
% Possibly one of the reasons could be that none of the suggested cognitive theories so far has accounted for differences among individuals, i.e.\ they only considered the data summed up with respect to the individual answer possibilities. 
% As recent investigations on psychological experiments show (cf.~\cite{khemlani:2016, ragni:2017}), it seems that different humans represent and reason about conditional information differently.
% This implies that \textit{the} human reasoner does not exist, instead there 
% seem to exist various (human) reasoning clusters.

@@

premises and one conclusion. 
The assertions are statements about properties over terms and can have one of the classical quantifiers in Table~\ref{table:moods}, which are called moods. The pair of syllogistic premises can have four different orders as shown in Table~\ref{t:2}. Based on these moods and orders, 64 different pairs of syllogistic premises can be constructed.

@@

@@

Consider the following pair of syllogistic premises: 

@@

concluded \emph{No chemists are artists} (29\%) and \emph{No valid conclusion} (27\%). The valid conclusion \emph{Some artists are not chemists}
under CL, was concluded by only 16\%, which is exactly the threshold, that the answer had not been chosen randomly~\cite{khemlani:2012}.

@@

Here, we focus on a qualitative assessment of the clustering approach in~\cite{declare:2017},
in the sense that we investigate the individual participants' conclusions with respect to the non-aggregated dataset provided by~\cite{khemlani:2016}.
In Section~\ref{sect:wcsclustering} and~\ref{sect:representing}, we introduce the underlying computational logic approach and the formal representation of cognitive principles within this approach. Section~\ref{sect:aggregateddata} illustrates an example and briefly discusses the performance of the approach in~\cite{declare:2017} on non-aggregated data.
Section~\ref{sect:nonag} provides a more adequate characterization of the individual's reasoning patterns.

@@

According to~\cite{declare:2017}, reasoning clusters can be expressed through cognitive principles and heuristic strategies. Cognitive principles are assumptions (not necessarily valid under CL) made by humans while reasoning, 
whereas heuristic strategies describe the methods that are applied when
conclusions are not derived by reasoning but instead based on structural patterns or {biases}.
The approach suggested in~\cite{declare:2017} is based on a new computational logic approach for human syllogistic reasoning~\cite{cogsci:2017}, which seems to perform better than other state-of-the-art cognitive theories when evaluated with aggregated data provided in~\cite{khemlani:2012}. 
The approach presented in~\cite{declare:2017} extended~\cite{cogsci:2017} by specifying three reasoning clusters and two heuristic strategies and achieved a match of 92\%, which was the highest result compared to the presented approaches in~\cite{khemlani:2012}.
% The system developed in~\cite{declare:2017}, was extended and participated at the Syllogism Challenge 2017.\footnote{\url{https://www.cc.uni-freiburg.de/modelingchallenge/challenge-2017}} 
Figure~\ref{overview:system:syllchal} illustrates the components of the system:
First, groups of reasoners were specified based on a set of underlying cognitive principles and heuristic strategies.
After that, this set was translated into a logic program (Section~\ref{sect:basic}-\ref{sect:advanced}), representing the group of reasoners.
Next, the desired models were computed (Section~\ref{sect:wcs}-\ref{sect:lfp}).
After that, the entailed relations between $a$ and $c$ were extracted (Section~\ref{sect:entail}). 
 The final answer distribution was specified according to the number of reasoning clusters 
that entailed the conclusion.
Finally, an illustrative representation of these clusters with respect to their distribution was done by means of multinomial process trees~\cite{Riefer1988}.

@@

\end{tikzpicture}
\caption{The system that participated at the Syllogism Challenge 2017\label{overview:system:syllchal}}

@@

We introduce an extension of WCS first presented in~\cite{dietz:hoelldobler:pereira:2017}. 
\textit{Contextual (logic) program clauses}
are expressions of the forms $A  \leftarrow  L_1 \land \ldots \land L_m \land
\cxt(L_{m+1}) \land \ldots \land \cxt(L_{m+p})$ (called
\textit{rules}), $A \leftarrow \top$ (called \textit{facts}), $A \leftarrow \bot$ (called
\textit{negative assumptions})\footnote{Under WCS, the negative
assumption will become $A \leftrightarrow \bot$, which, however, can be overwritten by other rules and facts (\textit{defeating} the assumption).} and $A \leftarrow \udf$ (called
\textit{unknown assumptions}), where
$A$ is an atom and~$L_i$ with~$1 \leq i \leq m+p$, is a literal.
$A$ is called \textit{head}
and $L_1 \land \ldots \land L_m \land
\cxt(L_{m+1}) \land \ldots \land \cxt(L_{m+p})$ as well as~$\top, \bot$
and $\udf$,
standing for \textit{true}, \textit{false} and \textit{unknown} respectively, are
called \textit{body} of the corresponding clauses.  A
\textit{contextual program}, denoted by $\mathcal P$,
is a finite set of contextual program clauses.
As we restrict terms to be either constants or variables only, we consider so-called \defname{data logic programs}.
If the clause contains variables, then they are implicitly universally quantified within the scope of the entire clause. 
% For instance, the clause $p(X) \leftarrow q(X)$ represents the formula $(\forall X) (p(X) \leftarrow q(X))$. Therefore, a clause never contains free variables.
A \defname{ground clause} is a clause that does not contain variables.
$\Ground \CalP$ denotes the set of all its ground clauses.
$A$ is \textit{defined in $\Ground \CalP$}  iff $\Ground \CalP$ contains a clause with head $A$.
The \textit{definition of $A$ in $\Ground \CalP$} is defined as $\Def(A,\CalP)
= \{ A \leftarrow \Body \mid A \leftarrow \Body \mbox{ is a clause
occurring in } \Ground \CalP\}$.
$A$ is \textit{undefined in $\Ground \CalP$} iff $A$ is not defined in $\Ground \CalP$.
The set of all atoms that are undefined in~$\Ground \CalP$ is denoted by~$\ud(\CalP)$.
Consider the following transformation for a given $\CalP$:
1.\ For each atom~$A$ defined in $\Ground \CalP$, replace
  all clauses of the form $A \leftarrow \Body_1, \ldots,$ $A \leftarrow
  \Body_m$ occurring in $\Ground \CalP$ by $ A \leftarrow \Body_1 \vee
  \ldots \vee \Body_m$. 2.\ Replace all occurrences of $\leftarrow$ by $\leftrightarrow$.
The obtained ground set of equivalences is called the \textit{weak completion}
of~$\CalP$ or~$\WC\CalP$.
% $\neg A$ is \textit{assumed in $\Ground \CalP$} iff $\Ground \CalP$
% contains a negative assumption with head $A$, $\Ground \CalP$ does not
% contain an unknown assumption with head $A$, and $\Def(A,\CalP) = \emptyset$.
We omit the word \textit{contextual} when we refer to programs, if not stated otherwise.

@@

We consider the three-valued {\L}ukasiewicz logic~\cite{lukasiewicz:20}
extended with the $\cxt$ connective, for which the
corresponding truth values are $\top$, $\bot$ and $\udf$, meaning \textit{true}, \textit{false}
and \textit{unknown}, respectively.
% As it seems,  $\cxt$ corresponds to {\L}ukasiewicz necessity operator~\cite{}, where the difference is, that $\cxt$ is restricted to be applicable to literals only.
A \defname{three-valued interpretation}~$I$ is a mapping from the set of
logical formulas to the set
of truth values~$\{ \true, \bot, \udf\}$, represented as a pair~$I~=~\langle I^\true,I^\bot \rangle$ of two disjoint sets of atoms:  $I^\true =  \{A \mid A \mbox{ is mapped to } \true \mbox{ under } I\}$ and $I^\bot = \{A \mid A \mbox{ is mapped to } \bot \mbox{ under } I \}$.
Atoms which do not occur in~$I^\true \cup I^\bot$ are mapped to~$\udf$.
The truth value of a given formula
under $I$ is determined according to the truth tables in
Table~\ref{tab:3vldluka}.
$I(F) = \top$ denotes that a formula $F$ is mapped to true under $I$.
A \defname{three-valued model} $\CalM$ of~$\CalP$ is a three-valued interpretation such that
$\CalM(A \leftarrow \Body) = \true$ for each $A \leftarrow \Body \in \Ground\CalP$.
Let $I = \langle I^\top, I^\bot \rangle$ and $J = \langle J^\top,
J^\bot \rangle$ be two interpretations.
$I \subseteq J$ iff $I^\top \subseteq J^\top$ and $I^\bot \subseteq J^\bot$. $I$ is the \textit{least model} of $\CalP$
iff for any other model~$J$ of $\CalP$ it holds that $I \subseteq J$.

\begin{table}[t]
\[\small
\begin{array}[c]{@{\hspace{0mm}}c|c}
F & \neg F\\ \midrule
\top & \bot \\
\bot & \top \\
\udf & \udf
\end{array}
\;\
\begin{array}{c|lll}
 \wedge & \top & \udf & \bot \\
\midrule
\top & \top & \udf & \bot \\
\udf & \udf & \udf & \bot \\
\bot & \bot & \bot & \bot
 \end{array}
\;\
\begin{array}{c|lll}
 \vee & \top & \udf & \bot \\
\midrule
\top & \top & \top & \top \\
\udf & \top & \udf & \udf \\
\bot & \top & \udf & \bot
 \end{array}
\;\
\begin{array}{c|lll}
\leftarrow & \top & \udf & \bot \\
\midrule
\top & \top & \top & \top \\
\udf & \udf & \top & \top \\
\bot & \bot & \udf & \top
 \end{array}
\;\
\begin{array}{c|ccc}
  \leftrightarrow  & \top & \udf & \bot \\
  \midrule
\top & \top & \udf & \bot \\
\udf & \udf & \top & \udf\\
\bot & \bot & \udf & \top
 \end{array}
\;\
\begin{array}{c|c}
 L & \cxt(L)\\
\midrule
\top & \top \\
\bot & \bot  \\
\udf & \bot
\end{array}
\]
\caption{The truth tables for the connectives under the three-valued {\L}ukasiewicz logic and for $\cxt$. $L$ is a literal, $\top$, $\bot$, and $\udf$ denote \textit{true}, \textit{false},
and \textit{unknown}, respectively.\label{tab:3vldluka}}
\end{table}

A set of \textit{integrity constraints} $\CalIC$ consists of clauses of
the form $\udf \leftarrow \Body$, where $\Body$ is a conjunction of
literals and $\udf$ denotes unknown. An interpretation maps
an integrity constraint to $\top$ iff $\Body$ is either mapped to
$\udf$ or $\bot$.  
Given an interpretation~$I$
and a set of integrity constraints~$\CalIC$,~$I$ \textit{satisfies}~$\CalIC$
iff all clauses in~$\CalIC$ are true under~$I$.

@@

Consider the following semantic operator~\cite{stenning:vanlambalgen:2008}: Let $I = \langle I^\top,I^\bot
\rangle$ be an interpretation. $\Phi_\CalP (I) =
\langle J^\top,J^\bot\rangle$, where
\[
\begin{array}{lcl}
J^\top & = & \{ A \mid A \leftarrow \Body \in \Def(A,\CalP)
\mbox{ and
} \Body \mbox{ is \True under } \langle I^\top,I^\bot \rangle \} \\
J^\bot & = & \{ A \mid \Def(A,\CalP) \neq \emptyset \mbox{ and }\\
&& \rule{7.5mm}{0mm}\Body \mbox{ is \False under } \langle
I^\top,I^\bot \rangle \mbox{ for all }  A \leftarrow \Body \in \Def(A,\CalP)\}.
\end{array}\Shrink
\]
The weak completion of non-contextual programs\footnote{Non-contextual programs refer programs that do not contain rules, in which $\cxt$ appears in the body of any rule, i.e.\ $p = 0$.} 
always has a least model under  {\L}ukasiewicz logic,
which can be computed by the least fixed point of~$\Svlp$\cite{hk:2009a}. The correspondence to other well-known logic programming approaches, in particular 
to the well-founded semantics has been shown in~\cite{dietz:hoelldobler:wernhard:2014}.

The weak completion of contextual
programs might have more than one minimal model, and it is not guaranteed that 
the least fixed point of $\Svlp$ always exists. However,
if these programs do not contain cycles, then there always exists a supported model, which 
corresponds to the least fixed point of~$\Svlp$~\cite{dietz:hoelldobler:pereira:2017,dietz:hoelldobler:philipp:2017}.
Let us denote the least fixed point of $\Svlp$ as $\CalM_\CalP$:
As the fixed point of $\Svlp$ is unique and only computes the supported minimal model of $\WComp\CalP$, we define
$\CalP \ModelsWCS F$ iff $\CalM_\CalP(F) = \top$.
For all programs considered in the sequel, $\CalM_\CalP$ exists.

@@

Eight principles for quantified statements have been developed in~\cite{cogsci:2017,costa:dietz:Hoelldobler:2017,declare:2017}.
In the following, the programs are
specified using the predicates $y$ and $z$, where~$yz$ can be replaced by $ab$, $ba$, $cb$, or $bc$ and depend on the figures shown in Table~\ref{t:2}. First, we introduce the basic principles that are assumed for all premises when applicable. Thus, we assume them to be assumed by all (human) reasoners. 
In Section~\ref{sect:advanced}, we present the advanced principles, which will 
later be used to distinguish between the clusters of reasoners.
% We indicate the cognitive principles in the text by specifying them in brackets.
A complete specification of the logic programs with respect to the moods according to all principles can be found in~\cite{declare:2017}.

@@

\subsubsection{Conditional Representation (\conditionals) and License for Inference (\licenses)}\label{sect:condli}
Consider \textit{All y are z} ({\MA yz}), which in CL, is represented as $\forall X (y(X) \rightarrow z(X))$.
Similarly, we assume that humans also understand this statement as a conditional sentence (\conditionals).
However, it seems that humans understand them defeasibly, they assume a \textit{license for the inference}~\cite{stenning:vanlambalgen:2008},
i.e.\ they might allow exceptions to the conditional (\licenses). For (\MA yz) this can be 
explicitly expressed by 
\textit{all $y$ that are not abnormal, are $z$}.
% \\
% Accordingly, $z(X)$ is conjoint with an abnormality predicate: 
% \[\forall X (y(X) \wedge \neg \Ab(X) \rightarrow z(X)).\] 
By default, we assume that \textit{nothing is abnormal}. % with respect to $X$}:
% \[
% \Ab(X) \leftarrow \bot.
% \]

@@

Consider the statement \textit{No y is z.} ({\ME yz}):
Similarly to the previous case, (\licenses) and (\import) apply here
as well.
The logic programs specified in Subsection~\ref{sect:wcs} 
do not allow heads of clauses to be negative literals. Therefore, a negative conclusion~$\neg p(X)$ is represented
by introducing an auxiliary formula $p'(X)$ together with the clause $p(X) \leftarrow \neg p'(X)$ and the integrity constraint $\udf \leftarrow p(X) \wedge p'(X)$ (\transformation). This is a widely used technique in Logic Programming (e.g. choice rules in~\cite{GebserKaminskiKaufmannSchaub12}). 
Another principle that we introduce is the no double negation principle: Under the Weak Completion Semantics, a positive conclusion can be derived from double negation appearing in two conditionals. However, it seems that humans normally do not reason in such a way~\cite{khemlani:2012}. Hence, we block them with the help of abnormalities (\dnegation). $\CalP_{Eyz}$, the logic program representing (\ME yz) is as follows:
% \footnote{For simplicity, we omitted to list the clauses that are introduced by the (\converse) principle in $\CalP_{Eyz}$: The same clauses just switching $y$ and $z$ are added and thus also the fact $z(o_2) \leftarrow \top$ for another object $o_2$.
% The entire program can be found in~\cite{declare:2017}.}
\begin{align}
 z'(X) & \leftarrow y(X) \wedge \neg \Ab_{ynz}(X).  \tag{\conditionals\ \&\ \transformation\ \&\  \licenses} \\
\Ab_{ynz}(X)  & \leftarrow \cxt(z(X)).\tag{\licenses} \\
z(X) & \leftarrow \neg z'(X) \wedge \neg \Ab_{nzz}(X). \tag{\transformation\ \&\ \licenses} \\
y(o_1) & \leftarrow \top. \tag{\import} \\
\Ab_{nzz}(o_1) & \leftarrow \bot. \tag{\licenses\ \&\  \dnegation}
\end{align}
As we now have both $z(X)$ and $z'(X)$ in the head of some clause, we need to add the 
following integrity constraints: $\udf \leftarrow z(X) \wedge
z'(X)$. We obtain 
\[\CalM_{\CalP_{Eyz}} = \langle \{y(o_1), z'(o_1)\},\{\Ab_{ynz}(o_1), \Ab_{nzz}(o_1),  z(o_1)\}
\rangle.
\]

>>>>

\usepackage[backgroundcolor=orange!5,bordercolor=orange,linecolor=orange,textsize=footnotesize]{todonotes}

@@

% Yet, the cognitive adequacy of a theory can only be measured, if that theory is evaluable, i.e.\ if the theory can uniformally account for episodes of human reasoning systematically, according to its underlying assumptions. 
% Only then, the cognitve adequacy of that theory can be compared to others.
% 
% Formal methods can offer the required tools to implement such cognitive theories. This in turn, can allow a new way of communication among the fields, by avoiding ambiguous definitions, showing their formal correspondences and finally providing appropriate evaluation methods with respect to their cognitive adequacy. 
% A major drawback of 
The results of the meta-study on syllogistic reasoning in~\cite{khemlani:2012} show that the answers given by humans do not only systematically differ from the valid conclusions under CL, but from any other proposed cognitive theory (cf.~\cite{BJ89,johnsonlaird:1983,Rips1994,Polk1995,chater:oaksford:1999}).
% Possibly one of the reasons could be that none of the suggested cognitive theories so far has accounted for differences among individuals, i.e.\ they only considered the data summed up with respect to the individual answer possibilities. 
% As recent investigations on psychological experiments show (cf.~\cite{khemlani:2016, ragni:2017}), it seems that different humans represent and reason about conditional information differently.
% This implies that \textit{the} human reasoner does not exist, instead there 
% seem to exist various (human) reasoning clusters.

@@

premises and one conclusion,
each of which is a statement about properties over terms which can have one of the classical quantifiess in Table~\ref{table:moods} (called \emph{moods}). The pair of syllogistic premises can have four different orders as shown in Table~\ref{t:2} (called \emph{figures}). Based on these moods and figures, 64 different pairs of syllogistic premises can be constructed.

@@

\todo[inline]{R: Für mich ist der letzte Satz unverständlich. Vorschlag: ``\dots each of these properties occurs in exactly one of the premises, and there is a third property connecting both premises which does not occur in the conclusion.''}\noindent%

@@

For instance, consider the following pair of syllogistic premises: 

@@

concluded \emph{No chemists are artists} (29\;\%) and \emph{No valid conclusion} (27\;\%).
The valid conclusion under CL, \emph{Some artists are not chemists},
was concluded by only 16\,\%, which is exactly the threshold that the answer had not been chosen randomly~\cite{khemlani:2012}.

@@

Here, we focus on a qualitative assessment of the clustering approach in~\cite{declare:2017},
in the sense that we investigate the individual participants' conclusions with respect to the non-aggregated dataset provided by~\cite{khemlani:2016}.
In Section~\ref{sect:wcsclustering} and~\ref{sect:representing}, we introduce the underlying computational logic approach and the formal representation of cognitive principles within this approach. Section~\ref{sect:aggregateddata} illustrates an example and briefly discusses the performance of the approach in~\cite{declare:2017} on non-aggregated data.
Section~\ref{sect:nonag} provides a more adequate characterization of the individuals' reasoning patterns.

@@

According to~\cite{declare:2017}, reasoning clusters can be expressed through cognitive principles and heuristic strategies. Cognitive principles are assumptions (not necessarily valid under CL) made by humans while reasoning, 
whereas heuristic strategies describe the methods that are applied when
conclusions are not derived by reasoning but instead based on structural patterns or {biases}.
The approach suggested in~\cite{declare:2017} is based on a new computational logic approach for human syllogistic reasoning~\cite{cogsci:2017}, which seems to perform better than other state-of-the-art cognitive theories when evaluated with aggregated data provided in~\cite{khemlani:2012}. 
The approach presented in~\cite{declare:2017} extended~\cite{cogsci:2017} by specifying three reasoning clusters and two heuristic strategies and achieved a match of 92\;\%, which was the highest result compared to the presented approaches in~\cite{khemlani:2012}.
% The system developed in~\cite{declare:2017}, was extended and participated at the Syllogism Challenge 2017.\footnote{\url{https://www.cc.uni-freiburg.de/modelingchallenge/challenge-2017}} 
Figure~\ref{overview:system:syllchal} illustrates the components of the system:
First, groups of reasoners were specified based on a set of underlying cognitive principles and heuristic strategies.
After that, this set was translated into a logic program (Section~\ref{sect:basic}-\ref{sect:advanced}), representing the group of reasoners.
Next, the desired\todo{R: desired? Entailed, oder was willst du sagen?} models were computed (Section~\ref{sect:wcs}-\ref{sect:lfp}).
After that, the entailed relations between $a$ and $c$ were extracted (Section~\ref{sect:entail}). 
 The final answer distribution was specified according to the number of reasoning clusters 
that entailed the conclusion.
Finally, an illustrative representation of these clusters with respect to their distribution was done by means of multinomial process trees~\cite{Riefer1988}.

@@

\end{tikzpicture}
\caption{The system that participated at the Syllogism Challenge 2017\label{overview:system:syllchal}.}

@@

We introduce an extension of WCS first presented in~\cite{dietz:hoelldobler:pereira:2017}. 
\textit{Contextual (logic) program clauses}
are expressions of the forms $A  \leftarrow  L_1 \land \ldots \land L_m \land
\cxt(L_{m+1}) \land \ldots \land \cxt(L_{m+p})$ (called
\textit{rules}), $A \leftarrow \top$ (called \textit{facts}), $A \leftarrow \bot$ (called
\textit{negative assumptions})\footnote{Under WCS, the negative
assumption will become $A \leftrightarrow \bot$, which, however, can be overwritten by other rules and facts (\textit{defeating} the assumption).} and $A \leftarrow \udf$ (called
\textit{unknown assumptions}), where
$A$ is an atom and~$L_i$ with~$1 \leq i \leq m+p$, is a literal.
$A$ is called \textit{head}
and $L_1 \land \ldots \land L_m \land
\cxt(L_{m+1}) \land \ldots \land \cxt(L_{m+p})$ as well as~$\top, \bot$
and $\udf$,
standing for \textit{true}, \textit{false} and \textit{unknown} respectively, are
called \textit{body} of the corresponding clauses.  A
\textit{contextual program}, denoted by $\mathcal P$,
is a finite set of contextual program clauses.
We restrict terms to be either constants or variables only, hence we consider so-called \defname{data logic programs}.
If a clause contains variables, then they are implicitly universally quantified within the scope of the entire clause. 
% For instance, the clause $p(X) \leftarrow q(X)$ represents the formula $(\forall X) (p(X) \leftarrow q(X))$. Therefore, a clause never contains free variables.
A \defname{ground clause} is a clause that does not contain variables.
$\Ground \CalP$ denotes the set of all ground clauses of $\CalP$.
An atom $A$ is \textit{defined in $\Ground \CalP$}  iff $\Ground \CalP$ contains a clause with head $A$.
The \textit{definition of $A$ in $\Ground \CalP$} is defined as $\Def(A,\CalP)
= \{ A \leftarrow \Body \mid A \leftarrow \Body \mbox{ is a clause
occurring in } \Ground \CalP\}$.
$A$ is \textit{undefined in $\Ground \CalP$} iff $A$ is not defined in $\Ground \CalP$.
The set of all atoms that are undefined in~$\Ground \CalP$ is denoted by~$\ud(\CalP)$.
Consider the following transformation for a given $\CalP$:
1.\ For each atom~$A$ defined in $\Ground \CalP$, replace
  all clauses of the form $A \leftarrow \Body_1, \ldots,$ $A \leftarrow
  \Body_m$ occurring in $\Ground \CalP$ by $ A \leftarrow \Body_1 \vee
  \ldots \vee \Body_m$. 2.\ Replace all occurrences of $\leftarrow$ by $\leftrightarrow$.
The obtained ground set of equivalences is called the \textit{weak completion}
of~$\CalP$ or~$\WC\CalP$.
% $\neg A$ is \textit{assumed in $\Ground \CalP$} iff $\Ground \CalP$
% contains a negative assumption with head $A$, $\Ground \CalP$ does not
% contain an unknown assumption with head $A$, and $\Def(A,\CalP) = \emptyset$.
We omit the word \textit{contextual} when we refer to programs, if not stated otherwise.

@@

\todo[inline]{R: Ist es eine Überlegung wert, \L ukasiewicz logic vor contextual programs einzuführen? Oben benutzen wir schon $\udf$, was erst hier eingeführt wird.}
We consider the three-valued {\L}ukasiewicz logic~\cite{lukasiewicz:20}
extended with the $\cxt$ connective, for which the
corresponding truth values are $\top$, $\bot$ and $\udf$, meaning \textit{true}, \textit{false}
and \textit{unknown}, respectively.
% As it seems,  $\cxt$ corresponds to {\L}ukasiewicz necessity operator~\cite{}, where the difference is, that $\cxt$ is restricted to be applicable to literals only.
A \defname{three-valued interpretation}~$I$ is a mapping from the set of
logical formulas to the set
of truth values~$\{ \true, \bot, \udf\}$, represented as a pair~$I~=~\langle I^\true,I^\bot \rangle$ of two disjoint sets of atoms:  $I^\true =  \{A \mid A \mbox{ is mapped to } \true \mbox{ under } I\}$ and $I^\bot = \{A \mid A \mbox{ is mapped to } \bot \mbox{ under } I \}$.
Atoms which do not occur in~$I^\true \cup I^\bot$ are mapped to~$\udf$.
The truth value of a given formula
under $I$ is determined according to the truth tables in
Table~\ref{tab:3vldluka}.
$I(F) = \top$ denotes that a formula $F$ is mapped to true under $I$.
A \defname{three-valued model} $\CalM$ of~$\CalP$ is a three-valued interpretation such that
$\CalM(A \leftarrow \Body) = \true$ for each $A \leftarrow \Body \in \Ground\CalP$.
Let $I = \langle I^\top, I^\bot \rangle$ and $J = \langle J^\top,
J^\bot \rangle$ be two interpretations.
$I \subseteq J$ iff $I^\top \subseteq J^\top$ and $I^\bot \subseteq J^\bot$. $I$ is the \textit{least model} of $\CalP$
iff for any other model~$J$ of $\CalP$ it holds that $I \subseteq J$.

\begin{table}[t]
\[\small
\begin{array}[c]{@{\hspace{0mm}}c|c}
F & \neg F\\ \midrule
\top & \bot \\
\bot & \top \\
\udf & \udf
\end{array}
\;\
\begin{array}{c|lll}
 \wedge & \top & \udf & \bot \\
\midrule
\top & \top & \udf & \bot \\
\udf & \udf & \udf & \bot \\
\bot & \bot & \bot & \bot
 \end{array}
\;\
\begin{array}{c|lll}
 \vee & \top & \udf & \bot \\
\midrule
\top & \top & \top & \top \\
\udf & \top & \udf & \udf \\
\bot & \top & \udf & \bot
 \end{array}
\;\
\begin{array}{c|lll}
\leftarrow & \top & \udf & \bot \\
\midrule
\top & \top & \top & \top \\
\udf & \udf & \top & \top \\
\bot & \bot & \udf & \top
 \end{array}
\;\
\begin{array}{c|ccc}
  \leftrightarrow  & \top & \udf & \bot \\
  \midrule
\top & \top & \udf & \bot \\
\udf & \udf & \top & \udf\\
\bot & \bot & \udf & \top
 \end{array}
\;\
\begin{array}{c|c}
 L & \cxt(L)\\
\midrule
\top & \top \\
\bot & \bot  \\
\udf & \bot
\end{array}
\]
\caption{The truth tables for the connectives under the three-valued {\L}ukasiewicz logic and for $\cxt$. $L$ is a literal and $\top$, $\bot$, and $\udf$ denote \textit{true}, \textit{false},
and \textit{unknown}, respectively.\label{tab:3vldluka}}
\end{table}

A set of \textit{integrity constraints} $\CalIC$ consists of clauses of
the form $\udf \leftarrow \Body$, where $\Body$ is a conjunction of
literals\todo{R: ``and $\udf$ denotes unknown'' entfernt, sollte an dieser Stelle klar sein}. An interpretation maps
an integrity constraint to $\top$ iff $\Body$ is either mapped to
$\udf$ or $\bot$.  
Given an interpretation~$I$
and a set of integrity constraints~$\CalIC$,~$I$ \textit{satisfies}~$\CalIC$
iff all clauses in~$\CalIC$ are true under~$I$.

@@

Consider the following semantic operator~\cite{stenning:vanlambalgen:2008}: Let $I = \langle I^\top,I^\bot
\rangle$ be an interpretation. $\Phi_\CalP (I) =
\langle J^\top,J^\bot\rangle$, where
\[
\begin{array}{lcl}
J^\top & = & \{ A \mid A \leftarrow \Body \in \Def(A,\CalP)
\mbox{ and
} \Body \mbox{ is \True under } \langle I^\top,I^\bot \rangle \} \\
J^\bot & = & \{ A \mid \Def(A,\CalP) \neq \emptyset \mbox{ and }\\
&& \rule{7.5mm}{0mm}\Body \mbox{ is \False under } \langle
I^\top,I^\bot \rangle \mbox{ for all }  A \leftarrow \Body \in \Def(A,\CalP)\}.
\end{array}\Shrink
\]
The weak completion of non-contextual programs\footnote{Non-contextual programs refer programs that do not contain rules in which $\cxt$ appears in the body of any rule, i.e.\ $p = 0$.} 
always has a least model under  {\L}ukasiewicz logic,
which can be computed by the least fixed point of~$\Svlp$\cite{hk:2009a}. The correspondence to other well-known logic programming approaches, in particular 
to the well-founded semantics has been shown in~\cite{dietz:hoelldobler:wernhard:2014}.

The weak completion of contextual
programs might have more than one minimal model, and it is not guaranteed that 
the least fixed point of $\Svlp$ always exists. However,
if these programs do not contain cycles, then there always exists a supported model\todo{R: Begriff ``supported model'' unklar}, which 
corresponds to the least fixed point of~$\Svlp$~\cite{dietz:hoelldobler:pereira:2017,dietz:hoelldobler:philipp:2017}.
Let us denote the least fixed point of $\Svlp$ as $\CalM_\CalP$:
As the fixed point of $\Svlp$ is unique and only computes the supported minimal model of $\WComp\CalP$, we define
$\CalP \ModelsWCS F$ iff $\CalM_\CalP(F) = \top$.
For all programs considered in the sequel, $\CalM_\CalP$ exists.

@@

Eight principles for quantified statements have been developed in~\cite{cogsci:2017,costa:dietz:Hoelldobler:2017,declare:2017}.
In the following, the programs are
specified using the predicates $y$ and $z$, where~$yz$ can be replaced by $ab$, $ba$, $cb$, or $bc$ and depend on the figures shown in Table~\ref{t:2}. First, we introduce the basic principles that are assumed for all premises when applicable. Thus, we assume them to be assumed\todo{R: assumed $\to$ applied?} by all (human) reasoners. 
In Section~\ref{sect:advanced}, we present the advanced principles, which will 
later be used to distinguish between the clusters of reasoners.
% We indicate the cognitive principles in the text by specifying them in brackets.
A complete specification of the logic programs with respect to the moods according to all principles can be found in~\cite{declare:2017}.

@@

\subsubsection{Conditional Representation (\conditionals) and License for Inference (\licenses)}\label{sect:condli}
Consider \textit{All y are z} ({\MA yz}), which in CL, is represented as $\forall X (y(X) \rightarrow z(X))$.
Similarly, we assume that humans also understand this statement as a conditional sentence (\conditionals).
However, it seems that humans understand them defeasibly, \todo{R: i.e.?} they assume a \textit{license for the inference}~\cite{stenning:vanlambalgen:2008},
i.e.\ they might allow exceptions to the conditional (\licenses). For (\MA yz) this can be 
explicitly expressed by 
\textit{all $y$ that are not abnormal are $z$}.
% \\
% Accordingly, $z(X)$ is conjoint with an abnormality predicate: 
% \[\forall X (y(X) \wedge \neg \Ab(X) \rightarrow z(X)).\] 
By default, we assume that \textit{nothing is abnormal}. % with respect to $X$}:
% \[
% \Ab(X) \leftarrow \bot.
% \]

@@

Consider the statement \textit{No y is z.} ({\ME yz}):
Similarly to the previous case, (\licenses) and (\import) apply here
as well.
The logic programs specified in Subsection~\ref{sect:wcs} 
do not allow heads of clauses to be negative literals. Therefore, a negative conclusion~$\neg p(X)$ is represented
by introducing an auxiliary formula $p'(X)$ together with the clause $p(X) \leftarrow \neg p'(X)$ and the integrity constraint $\udf \leftarrow p(X) \wedge p'(X)$ (\transformation). This is a widely used technique in Logic Programming (e.g. choice rules in~\cite{GebserKaminskiKaufmannSchaub12}). 
Another principle that we introduce is the \emph{no double negation} principle: Under the Weak Completion Semantics, a positive conclusion can be derived from double negation appearing in two conditionals. However, it seems that humans normally do not reason in such a way~\cite{khemlani:2012}. Hence, we block them with the help of abnormalities (\dnegation). $\CalP_{Eyz}$, the logic program representing (\ME yz) is as follows:
% \footnote{For simplicity, we omitted to list the clauses that are introduced by the (\converse) principle in $\CalP_{Eyz}$: The same clauses just switching $y$ and $z$ are added and thus also the fact $z(o_2) \leftarrow \top$ for another object $o_2$.
% The entire program can be found in~\cite{declare:2017}.}
\begin{align}
 z'(X) & \leftarrow y(X) \wedge \neg \Ab_{ynz}(X).  \tag{\conditionals\ \&\ \transformation\ \&\  \licenses} \\
\Ab_{ynz}(X)  & \leftarrow \cxt(z(X)).\tag{\licenses} \\
z(X) & \leftarrow \neg z'(X) \wedge \neg \Ab_{nzz}(X). \tag{\transformation\ \&\ \licenses} \\
y(o_1) & \leftarrow \top. \tag{\import} \\
\Ab_{nzz}(o_1) & \leftarrow \bot. \tag{\licenses\ \&\  \dnegation}
\end{align}
As we now have both $z(X)$ and $z'(X)$ in the head of some clause, we need to add the 
following integrity constraints: $\udf \leftarrow z(X) \wedge
z'(X)$. We obtain 
\[\CalM_{\CalP_{Eyz}} = \langle \{y(o_1), z'(o_1)\},\{\Ab_{ynz}(o_1), \Ab_{nzz}(o_1),  z(o_1)\}
\rangle.
\]
